%% start of file `template.tex'.
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\documentclass[11pt,a4paper,sans]{moderncv}   

% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{classic}
% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{blue}                          

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\firstname{\textcolor{firstNameColor}{Ravikiran}}
\familyname{\textcolor{familyNameColor}{Janardhana}}
\address{513 CENTRAL AVE, APT T}{MOUNTAIN VIEW, CA 94043}
\mobile{(919)-448-8740}
\email{rkjanardhana@gmail.com}
\homepage{https://www.ravikiranj.net}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\begin{document}
% Define Colors
\definecolor{firstNameColor}{rgb}{0.45,0.45,0.45}
\definecolor{familyNameColor}{rgb}{0.60,0.60,0.60}
% Personal information is controlled by variable called color2 as per https://tex.stackexchange.com/questions/111856/how-to-change-the-color-of-symbols-mobile-email-homepage-etc-in-moderncv
\definecolor{color2}{rgb}{0.30,0.30,0.30}

% Resume
\maketitle
% Work Experience
\section{Work Experience}
\cventry{2013-Present}{Software Engineer II}{TripAdvisor}{San Francisco}{}{
\begin{itemize}
\item{Currently working as a full stack engineer on Vacation Rentals Supply team.} 
\item{Worked on the Internal API and Mobile Web team as a full stack engineer for 3 yrs.}
\item{Improved performance of several internal APIs by 10-30\% with several layers of caching.}
\end{itemize}}

\vspace{1mm}

\cventry{Summer 2012}{Software Developer Intern}{Microsoft Corporation}{Redmond}{}{
\begin{itemize}
\item{Developed and implemented an algorithm based on AdaBoost (Adaptive Boosting) technique to detect multiple intents (or actions) in natural spoken language.} 
\end{itemize}}

\vspace{1mm}

\cventry{2009--2011}{Software Engineer}{Yahoo! India}{Bangalore}{}{
\begin{itemize}
\item{Developed Facebook, Twitter and LinkedIn modules for My Yahoo! product.} 
\end{itemize}}

% Education
\section{Education}
\cventry{2011-2013}{MS.}{University of North Carolina at Chapel Hill}{Chapel Hill, NC}{}{}
\cvline{}{Masters in Computer Science}

\vspace{1mm}

\cventry{2005--2009}{BE.}{Peoples Education Society Institute of Technology (PESIT)}{Bangalore, India}{Bachelor of Engineering in Computer Science, \textbf{University Topper}}{}

% Technical Skills
\section{Technical Skills}
\cvline{Programming}{Java, C/C++, Python}
\cvline{Web}{HTML5, Javascript, CSS, jQuery}
\cvline{Database}{PostgreSQL, MySQL}
\cvline{Platforms}{Linux, Windows}

% Projects
\section{Projects}
\cventry{Summer 2017}{SQL Viewer Chrome extension}{}{https://goo.gl/NAfHuw}{}{}

\cventry{2014-present}{Hipchat Bot (hbot)}{}{}{}{
\begin{itemize}
\item{Based on hubot and boosting developer productivity since 2014.}
\end{itemize}
}

\vspace{1mm}

\cventry{Spring 2012}{Twitter Sentiment Analyzer}{}{https://goo.gl/wzp8Zo}{}{
\begin{itemize}
\item{Developed a tool to analyze the sentiment expressed in a user's twitter status messages.}
\end{itemize}
}

% Technical Writing and Open Source
\section{Technical Writing and Open Source}
\cvline{Tech Blog}{\url{https://www.ravikiranj.net}}
\cvline{GitHub}{\url{https://github.com/ravikiranj}}
\end{document}

